Fusion Moves for Correlation Clustering

### 2014-11-06 paper/egpaper_for_review.tex
energy based hc section

@@

So far we only enforce must link constraints to obtain smaller problems.
One can also enforce must-not link constraints to the problem. 
If those are closed, they automatically lead to a decomposition of the problem, which is a interesting property for very huge data.

>>>>

\section{Energy Based Hierarchical Clustering (EBHC)}

Hierarchical clustering can be used to find approximate
solutions for correlation clustering.
In each step, the edge with the highest weight $w$ is
contracted (red edges in fig. ~\ref{fig:hc_alg}).
Doing so, parallel edges edges can occur.
Whenever there are multiple edges between 
a pair of nodes, these edges are merged into a single edge
by summing up their weights.
The algorithm stops if the highest edge weight is
smaller or equal to zero  (green edge in fig. ~\ref{fig:hc_alg}). Any further edge
contraction leads to worse energies.

Given the intrinsic greediness of hierarchical clustering, 
we do not expect very good solutions, but still a good starting 
point for move making algorithm as CGC \cite{beier_2014_cvpr}.
Therefore we propose to initialize  CGC with EBHC
and hope speedup of CGC.

Furthermore, we propose a algorithm to combine / fuse together
multiple EBHC results from perpetuated energies.
This algorithm, namely

\input{inputs/fig_hc_alg.tex} Correlation-Clustering-Fusion (CCF) Moves 
will be discussed in the following section.

@@

So far we only enforce must link constraints to obtain smaller problems.
One can also enforce cannot link constraints to the problem. 
If those are closed, they automatically lead to a decomposition of the problem, 
which is a interesting property for very huge data.
